Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-17 article-models-ttinternal.tex
reorganizing section 2.3

\subsection{Extension-weakening algebras}
The notion of (extension-)weakening algebra is dependent on the notion of extension algebra.
Although it is strictly speaking not dependent on the notion of empty-algebra,
we shall only formulate a weakening algebras in the setting of an
extension-empty algebras. When one wants to have a weakening operation which
also acts on the level of contexts in an extension algebra without empty
context, extra work has to be done to introduce these separately.

@@

>>>>

\subsection{Weakening algebras}
The notion of (extension-)weakening algebra is dependent on the notion of extension algebra.
Although it is strictly speaking not dependent on the notion of empty-algebra,
we shall only formulate a weakening algebras in the setting of an
extension-empty algebras. When one wants to have a weakening operation which
also acts on the level of contexts in an extension algebra without empty
context, extra work has to be done to introduce these separately.

@@

\subsection{Term-algebras}
Until now we had no need to consider term-algebras. Extension is an operation
letting contexts and families interact, the empty object is a term which
requires that contexts and families are compatible and weakening is an operation
which takes families to extended families. However, we need to consider
the notion of term-algebras before we can go into the internalization of
substitution. In this subsection we will define the notion of term-algebras
with extension and an empty object (which are simply called term-algebras),
term-homomorphisms between them and weakening term-algebras with their
homomorphisms.
